The designed method requires to compute arithmetic operations in $\Zomega$. Therefore, we have chosen Python-based programming language SageMath for the implementation of the extending window method as it contains many ready-to-use mathematical structure.  Using SageMath is very convenient as it also offers easily usable data structures or tools for plotting. Thus the code is more readable and we may focus on the algorithmic part of problem. On the other hand, SageMath is considerably slower than for example C++ or other low-level languages. Nevertheless, it is sufficient for our purpose.

The implementation is object-oriented. It consists of four classes. Class \emph{AlgorithmForParallelAddition} contains structures for computations in $\Zomega$. Specifically, we use the provided class \emph{PolynomialQuotientRing} to represent elements of $\Zomega$ and  \emph{NumberField} for obtaining numerical complex value of them. The class also links necessary instances and functions to construct algorithm for parallel addition by the extending window method for an algebraic integer $\omega$ given by its minimal polynomial $p$ and approximate complex value, a base $\beta\in\Zomega$, an alphabet $\A\subset\Zomega$ and input alphabet $\B$. Phase 1 of the extending window method is implemented in class \emph{WeightCoefficientsSetSearch} and Phase 2 in \emph{WeightFunctionSearch}. Class \emph{WeightFunction} holds the weight function $q$ computed in Phase 2. All classes are described in the following sections including lists of the important methods  with a short description. Sometimes, the notation from Chapter \ref{chap:methodDescription} is used for better understanding. For all implemented methods, see commented source code.  

Basically, weight function can be found just by creating an instance of \emph{AlgorithmForParallelAddition} and calling \textbf{findWeightFunction()}. For more comfortable usage, our implementation includes two interfaces -- a shell version and graphic user interface using interact in SageMath Cloud. The whole implementation is on the attached DVD or it can be downloaded from  \url{https://github.com/Legersky/ParallelAddition}.

\section{Class AlgorithmForParallelAddition}
\input{AlgorithmForParallelAddition.tex}


\section{Class WeightCoefficientsSetSearch}
\input{WeightCoefficientsSetSearch.tex}


\section{Class WeightFunctionSearch}
\input{WeightFunctionSearch.tex}


\section{Class WeightFunction}
\input{WeightFunction.tex}

\section{User interfaces}
We provide two interfaces for running of the implemented extending window method -- the~shell version and graphic user interface.

\subsection{Shell}
SageMath must be installed. The implementation of the extending window method is launched in a shell by typing \verb+sage extending_window_method.sage <input_sample.sage>+. The parameters of the numeration system and setting of outputs and computation is given by the SageMath file \verb+input_sample.sage+. See Appendix \ref{app:inputSample} for an example of such a file.

The name of the numeration system, minimal polynomial of generator $\omega$, an approximate value of $\omega$, the base $\beta$, alphabet $\A$ and input alphabet $\B$ are set in the part INPUTS. The maximum number of iterations in Phase 1, maximal length of the window in Phase 2 and the launching of the sanity check are set in SETTING. 

The boolean values in the part SAVING determines which formats of the outputs are saved. All outputs are saved in the folder \verb+./outputs/<name>/+. General information about the computation can be saved in the TeX format, the computed weight function and local digit set conversion in the CSV file format. An inputs setting saved as a dictionary can be loaded by the interact interface. The log of the whole computation can be saved as a text file. There is also an option to save unsolved combinations in Phase 2 in the CSV file format in the case of the interruption of the program.

According to the boolean values in the part IMAGES, figures of the alphabet, input alphabet, weight coefficients set or part of the set $\Zomega$ with marked alphabet shifted into points which are divisible by the base $\beta$ are saved in the PNG format to the folder \verb+./outputs/<name>/img/+. Optionally, the weight coefficients set is plotted with the  bound given by the proof of Theorem~\ref{thm:suffCondPhase1}. Images of individual steps of both phases of the extending window method can be saved, too. For Phase 2, the search for the weight coefficient  is plotted for the digits given by \verb+phase2_input+.  

The program prints out all inputs and then it computes the weight function $q$ by calling \fun{findWeightFunction}{ max\_iterations, max\_input\_length}. The increments of the weight coefficients set in each iteration of Phase 1 are printed and then also the obtained weight coefficients set $\Q$. The longest tested combinations given by repetition of one letter are printed after the computation of \fun{check\_one\_letter\_inputs}{max\_input\_length}. During computing of Phase 2, the current length of window and the number of saved combinations are printed. At the end, the final length of window, elapsed time and info about saved outputs are printed.  

It is possible to batch process all input files in one folder by executing the bash script \verb+ewm_batch <folder_name>+.  

\subsection{Interact in SageMath Cloud}
The graphic user interface is implemented using an interact in SageMath Cloud. The parts of the interact are on Figure \ref{fig:interact1}, \ref{fig:interact2} and \ref{fig:interact3} in Appendix \ref{app:interact}. The functionality is basically the same as the shell version. An account on the website \url{https://cloud.sagemath.com} is needed to use the interact. Create a new project and load files \verb+extending_window_method_GUI.sagews+ and \verb+interact_ewm.sage+. After executing of the cell by Shift+Enter in the first one, the parameters of the numeration system are filled in the corresponding spaces or one of the previous settings is loaded by typing its name.  By default, the last inputs are shown in the form. The inputs are submitted by pressing the button Update. Using check-boxes, the formats for saving of the output are chosen and the search for the weight function is launched by pressing second button Update.

The printed output is similar to the shell output. In addition, it contains figures and it is formatted using \LaTeX. Moreover, the sanity check can be run for a given length, the weight coefficient for a tuple of  input digits is returned or images of individual steps of both phases are shown and saved.